---
title: "Plotly Examples"
output: 
  html_document:
    toc: true
    toc_float: true
---


# Examples of Plotly

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	message = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

# Load libraries 

```{r load_libraries, message = FALSE}
library(tidyverse)
library(p8105.datasets)

library(plotly)
```


# Load Dataset 

Load the instacart dataframe. We'll only look at the most popular departments: produce, dairy eggs, snacks, beverages. 

```{r load_data}
data(instacart)
insta_df = instacart |>
#  filter(department %in% c("produce", "dairy eggs", "snacks", "beverages","pets")) |>
  select(department, aisle, order_dow, order_hour_of_day, days_since_prior_order, order_id, reordered, add_to_cart_order) |>
  mutate(order_dow = recode(order_dow,  "0"="Sunday",
       "1"="Monday",
       "2"="Tuesday",
       "3"="Wednesday",
       "4"="Thursday",
       "5"="Friday",
       "6"="Saturday")) |>
  mutate(order_dow = as.factor(order_dow)) 

```

  instacart |> group_by(department) |>
  summarize(n_obs = n()) |>
  arrange((n_obs))

produce         409087
 2 dairy eggs      217051
 3 snacks          118862
 4 beverages       114046

# Barchart

Looking at frequency items are ordered from given aisles within those departments. The barchart below shows only aisles with >1,000 items ordered. 

```{r aisle_counts}
insta_df |> 
  filter(department %in% c("produce", "dairy eggs", "snacks", "beverages","pets")) |>
  count(aisle) |> 
  mutate(aisle = fct_reorder(aisle, n)) |> 
  filter(n > 1000) |>
  plot_ly(x = ~aisle, y = ~n, color = ~aisle, type = "bar", colors = "viridis")
```



```{r}
insta_df |>
  filter(department %in% c("produce", "dairy eggs", "snacks", "beverages","pets")) |>
  group_by(order_dow, department) |>
  summarize(n = n()) |>
  plot_ly(x = ~order_dow, y = ~n, type = "scatter", mode = "line", color = ~department, colors = "viridis")
```


nyc_airbnb |>
  mutate(text_label = str_c("Price: $", price, "\nRating: ", rating)) |>
  plot_ly(x = ~lat, y = ~long, color = ~price, alpha = 0.5,type = "scatter", mode = "markers", text = ~text_label)
  

```{r}
insta_df |> 
  filter(order_dow == "Monday") |>
  mutate(department = fct_reorder(department, add_to_cart_order)) |> 
  plot_ly(y = ~add_to_cart_order, color = ~department, type = "box", colors = "viridis")
```


# Ratio of reordered
```{r reorder}
insta_df |>
  group_by(department) |>
  summarize(mean = mean(reordered)) |>
  plot_ly(x = ~department, y = ~mean, type = "scatter", mode = "lines")

```

```{r add_to_cart}
insta_df |>
  filter(department %in% c("snacks","produce")) |>
  group_by(department, add_to_cart_order) |>
  summarize(mean = mean(reordered)) |>
  plot_ly(x = ~add_to_cart_order, y = ~mean, type = "scatter", mode = "lines", color = "department")


# Scatter Plot - Order day of week X Order hour of the day 
```

```{r}
#insta_df |>
#  filter(department == "produce") |>
 # plot_ly(x = ~aisle, y = ~days_since_prior_order, type = "scatter", mode = "markers")
  
```

```{r}



```

